Manuscript

### 2023-05-26 Manuscript1.Rmd
updates

```{r parameters visualization, fig.height=10, fig.width=10}
dd = get_experiment()

@@

RW_logistic = RW_logistic_vis(dd)
```

@@

@@

######################################### Kalman

mu_sigmaEta = rep(0.1,100)
mu_sigmaPsi = 0.1
mu_sigmaEpsilon = 2
sd_sigmaEta = 0.1
sd_sigmaPsi = 0.1
sd_sigmaEpsilon = 0.1
nsubs = 10
parameters = expand.grid(mu_sigmaEta = mu_sigmaEta,
                         mu_sigmaPsi = mu_sigmaPsi,
                         mu_sigmaEpsilon = mu_sigmaEpsilon,
                         sd_sigmaEta = sd_sigmaEta,
                         sd_sigmaPsi = sd_sigmaPsi,
                         sd_sigmaEpsilon = sd_sigmaEpsilon,
                         nsubs = nsubs)
parameters$id = 1:nrow(parameters)
data_list_kalman <- split(parameters, parameters$id)

@@

```{r}
mu_alpha = seq(0.1,0.5, length.out = 5)
kappa_alpha = seq(10,100, length.out = 2)

>>>>

```{r parameters visualization, fig.height=10, fig.width=12}
dd = get_experiment()

@@

#RW_logistic = RW_logistic_vis(dd)
```

@@

```{r parameter recovery for logistic}
mu_alpha = seq(0.1,0.5, length.out = 5)
kappa_alpha = seq(10,100, length.out = 2)

@@

######################################### logistic RW

@@
